Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-04-10 scnn.tex
update plot list
include figures in tex

@@

@@

Figure heaplix pooling.

@@

Figure our harmonics.

@@

Example on the heat equation
Figure filters
Figure diffusion (unit of heat)

@@

Figure: part map plot

@@

Figure: Filter if they look good.

>>>>

\subsection{Healpix sampling}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/healpix-3layers.jpg}
\caption{3 smaller sclales of the healpix sampling.}
\label{fig:healpix_sampling}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{figures/healpix_graph_4.pdf}
\includegraphics[width=0.45\textwidth]{figures/half_graph_4.pdf}
\caption{Left: Healpix graph for the full sphere using a nside parameter of $4$. Right: Top view of a Healpix graph for half the sphere using a nside parameter of $4$.}
\label{fig:healpix_graph_4}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/pooling.pdf}
\caption{Pooling, 1/12 of the sphere, 2 levels, molview projection.}
\label{fig:pooling}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/eigenvectors.pdf}
\caption{12 first graph Fourier eigenvectors.}
\label{fig:graph_harmonics}
\end{figure}

@@

Example on the heat equation
\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_sphere.pdf}
\caption{Top: Diffusion of a unit of heat for different time using the graph. Bottom: gaussian filtering on the sphere. Relative difference of the two diffusions: $13.5$\%, $6.1$\%, $5.2$\%, $3.8$\% }
\label{fig:gaussian_filters_comparizon}
\end{figure}

Figure filters 3 representations for both graph + spherical Fourier
\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_spectral.pdf}
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_gnomonic.pdf}
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_section.pdf}
\caption{3 Different effet visualization of filters. Top: Graph spectral domain. Middle: gnomonic projection on the sphere. Bottom: section of filter.}
\label{fig:gaussian_filters_visualization}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{figures/index_plotting_order20_nside16.pdf}

\caption{Indexes selected for the section ploting of the filter.}
\label{fig:index_section}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{figures/smooth_map_class_1.pdf}
\includegraphics[width=0.45\textwidth]{figures/smooth_map_class_2.pdf}
\caption{One sample of each class }
\label{fig:map_sample}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{figures/part_sphere.pdf}
\caption{3 subparts of the sphere with different sizes. Blue: order 1. Green: order 2. Yellow: order 3.}
\label{fig:subpart_sphere}
\end{figure}

@@

Figure: Filters 1D and Gnonomic
